---
title: "Project 2"
author: "Name Surname | Student_Number"
output:
  html_notebook: default
  pdf_document: default
---

<hr>

1.  Suppose `X` is a continuous random variable with pdf $f(x) = 3x^2,$ for $−1 < x < 0.$ Use R to:

    -   Find the probability that `X` is greater than -0.6.
    -   Find the conditional probability that `X` is lower than -0.5 given that `X` is greater than -0.8.
    -   Find the expectation and variance of `X`.

```{r}
# replace this comment with your code
```

2.  Suppose `X` is a normal distribution with mean 3 and variance 10. Use R to:

    -   Find the conditional probability that `X` \< 4 given that `X` \> 1.
    -   Find the value of `x1` such that the probability that `X` \> `x1` is 0.13.
    -   Simulate a sample of size `n` = 1000 from `X` and calculate the absolute difference between a sample estimate of the probability that `X` \> 3.5 and its corresponding true value.

```{r}
# replace this comment with your code
```

3.  The width of bolts of fabric (`X`) is normally distributed with unknown mean and variance. A dataset containing a sample of `X` called `bwidth` can be loaded using the following code:

```{r}
load(url('https://acaimo.github.io/teaching/data/bwidth.RData'))
```

Complete the following task using R to:

-   Visualise the distribution of the dataset.
-   Estimate the sample mean and sample variance of `X`.
-   Estimate the 95% confidence intervals for the mean and variance of `X`.
-   Simulate a new sample of size `n` = 50 from `X` (using the sample variance of `bwidth` sample) and test (`alpha` = 0.05) the hypothesis that the mean is equal to 950mm against the alternative that the mean is different from 950mm. Draw your conclusion automatically using an `if()` function.

```{r}
# replace this comment with your code
```

<hr>
